XXX

### 2012-03-25 paper/engNERwiki.tex
E.

The paper is structured as follows. XXX In section~\ref{sec:hun}, we show how the algorithm was adapted to Hungarian.

@@

\section{Data Description}

@@

\section{Evaluation}

@@

\section{Conclusions and Future Work}

>>>>

The paper is structured as follows. In section~\ref{sec:related} we overview related works. Section~\ret{sec:create} introduces our XXX algorithm; section~\ref{sec:hun}, shows how it was adapted to Hungarian. The corpus format is described in section~\ref{sec:data}. Section~\ref{sec:eval} contains the evaluation and section~\ref{sec:conclusion} our conclusions.

@@

\section{Data Description}
\label{sec:data}

@@

\section{Evaluation}
\label{sec:eval}

@@

\section{Conclusions and Future Work}
\label{sec:conclusion}
